Demes: a specification for interchanging complex demography

### 2022-04-08 paper.tex
add hudson and tajima refs

Within a population, we implicitly assume that allele frequency dynamics can
be described by the Wright-Fisher model.
Briefly, generations are non-overlapping (all parents
reproduce and die simultaneously) and the expected frequency (at birth)
of the $i^{th}$ allele currently at frequency $p_i$
one generation in the next generation is $p_iw_i/\bar{w}$,
where $w_i$ and $\bar{w}$ are the marginal and
mean fitnesses, respectively, properly weighted according to ancestry proportions.
In this framework,
a forward-time simulation of finite populations is equivalent
to multinomial sampling of allele frequencies each
generation (\citet[][pp 29-31]{burger2000-ul}, \citet[][pp 179-181]{crowkimura1970}),
and a backwards-time (coalescent) simulation follows the approximations
described in \cite[][chapter 3]{wakeley2008-hd}.
Further, this model assumes ``soft'' selection \citep{christiansen1975hard},
meaning that the dynamics of population sizes
changes are \textit{independent} of the details of individual fitnesses.
% In the \texttt{Discussion}, we discuss alternative models compatible
% with this framework and outline the expectations for tools implementing
% them.
\aprcomment{As such, this model excludes scenarios such as ``hard selection,''
in which population sizes are dependent on a population's mean fitness, or
stochastic fluctuations in population size, such as defining ``carrying capacities''.}
Many forwards and backwards time simulators currently implement this model
\citep[e.g.,][\aprcomment{and more\dots?}]{hudson2002generating,gutenkunst2009inferring,excoffier2011fastsimcoal,jouganous2017inferring,haller2019slim,thornton2019-nu}.
Each has their own unique method of specifying the details of selection and demography.
The goal of \Demes\ is to provide a common method for the latter task.

>>>>

Within a population, we implicitly assume that allele frequency dynamics can
be described by the Wright-Fisher model.
Briefly, generations are non-overlapping (all parents
reproduce and die simultaneously) and the expected frequency (at birth)
of the $i^{th}$ allele currently at frequency $p_i$
one generation in the next generation is $p_iw_i/\bar{w}$,
where $w_i$ and $\bar{w}$ are the marginal and
mean fitnesses, respectively, properly weighted according to ancestry proportions.
In this framework,
a forward-time simulation of finite populations is equivalent
to multinomial sampling of allele frequencies each
generation (\citet[][pp 29-31]{burger2000-ul}, \citet[][pp 179-181]{crowkimura1970}),
and a backwards-time (coalescent) simulation follows the approximations
described in \citet{tajima1983evolutionary,hudson1983testing}
and \citet[][chapter 3]{wakeley2008-hd}.
Further, this model assumes ``soft'' selection \citep{christiansen1975hard},
meaning that the dynamics of population sizes
changes are \textit{independent} of the details of individual fitnesses.
% In the \texttt{Discussion}, we discuss alternative models compatible
% with this framework and outline the expectations for tools implementing
% them.
\aprcomment{As such, this model excludes scenarios such as ``hard selection,''
in which population sizes are dependent on a population's mean fitness, or
stochastic fluctuations in population size, such as defining ``carrying capacities''.}
Many forwards and backwards time simulators currently implement this model
\citep[e.g.,][\aprcomment{and more\dots?}]{hudson2002generating,gutenkunst2009inferring,excoffier2011fastsimcoal,jouganous2017inferring,haller2019slim,thornton2019-nu}.
Each has their own unique method of specifying the details of selection and demography.
The goal of \Demes\ is to provide a common method for the latter task.
